\ttitle

### 2013-05-14 Chapters/Chapter2.tex
Add introduction Chapter 2

>>>>

\section{Statistical framework}
Many applications require the detection of time points at which the underlying properties of a system change.
This problem thus has received a lot of attention in the fields of data mining, etc... *** list and refs ***.
Often this problem is formulated in a statistical framework, by inspecting the data generating PDF (Probability Density Function) of the time series data.
A change point is then defined as a significant change in the properties of the PDF, such as the mean and variance.

The widely used CUSUM (cumulative sum) method by Basseville \etal \cite{basseville1993detection}, and the GLR (Generalized Likelihood Ratio) by Gustafsson \cite{gustafsson1996marginalized,gustafsson2000adaptive} take this approach.
The former originates from control methods for detection from bench marks.
The latter compares the logarithm of the likelihood ratio over two consecutive intervals.
These two methods is discussed and analyzed in section \ref{cusum-glr}.

The GLR method, as with others, relies on pre-specified parametric model assumptions and considers the data be independent over time, which makes it less flexible to real-world applications.
The proposed methods by Kawahara \etal \cite{kawahara2009change} and Lui \etal \cite{liu2013change} try to overcome these problems by estimating the \emph{ratio} between the PDF, instead of estimating each PDF.
This approach is discussed and analyzed in section \ref{density-ratio}.

The density-estimation methods, as with the GLR, rely on the log-likelihood ratio between PDFs.
The method of Camci \cite{camci2010change} takes an other approach within the statistical framework, by using a SVM (Support Vector Machine).
One problem it tries to overcome is the (claimed) weakness of many methods to detect a decrease in variance.
The method represents the distribution over the data points as a hyper-sphere in a higher dimension using kernel trick.
A change in the PDF is represented by a change in the radius of this sphere.
Section \ref{svm} discusses the SVM-method.

The final method under consideration, change detection via (intrinsic) dimensionality reduction, takes a different point of view.
Opposed to the other discussed methods, dimensionality reduction is framed in the MDL (Minimum Description Length) framework.
It uses the estimated underlying number of parameters of the time series as a model for change detection.
Section \ref{dim-reduction} discuses this method.

%----------------------------------------------------------------------------------------
% CUSUM and GLR
\input{./Chapters/Chapter2/cusum_glr}

%----------------------------------------------------------------------------------------
% Density Ratio Estimation
\input{./Chapters/Chapter2/density_ratio}

%----------------------------------------------------------------------------------------
% Support Vector Machines
\input{./Chapters/Chapter2/svm}

%----------------------------------------------------------------------------------------
% Dimensionality reduciton
\input{./Chapters/Chapter2/dim_reduction}
